### 2014-04-22 docs/paper/paper.tex
power and temperature

@@

\subsection{power, \% timestep used for each simulation, \% of board resources for each simulation}

>>>>

Power analysis showed that the implemented design, with 7 one-dimensional and 7 two-dimensional population units,
is estimated to use a maximum of 5.675~W of power while a simulation is running, assuming all population units are fully utilized.
With the installed heatsink and fan on the VC707 board, the FPGA is expected to operate at an on-die temperature of $31.5\,^{\circ}{\rm C}$.

@@
